%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Assignment 4.2: Testing hypotheses about a correlation by hand
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\handassignment{Assignment 4.2: Testing hypotheses about a correlation by hand}

The store manager looks at the results of her calculations and sees some potential for increasing the sales of her branch. However, before she starts spending more money on advertising in these to hard-to-reach neighborhoods, she wants to gain reasonable assurance that her results can be generalized to all of her potential customers. Therefore, she wants to test the hypothesis that, with 95\% confidence, this \concept{correlation} is truly negative in the entire \concept{population} of customers. \\

\question{
    4.2 a
}{
    Formulate the \concept{null hypothesis} $H_0$ and \concept{alternative hypothesis} $H_1$ for the manager’s test of the \concept{population correlation coefficient} $\rho_{xy}$.  
}

\hint{Hint 4.4: Think about whether this is a one-sided test or a two-sided test?}

\hypothesesbox{4.2a}

\question{
    4.2 b
}{
    Write down the relevant information that appeared in assignment 4.1. Use the symbols $N$, $n$, $r_{xy}$, $\rho_{xy}$
}

\hint{Hint 4.5: Not all symbols are known.}

\emptyanswerbox{
    4.2b
}{
        $N$: \shortanswerline \hspace{1cm} \quad $r_{xy}$: \shortanswerline
            \answerbreak
            \hspace*{1pt}$n$: \shortanswerline \hspace{1cm} \quad $\rho_{xy}$: \shortanswerline
}

\question{
    4.2 c
}{
    Find out the \concept{critical z-value} that is required to reject $H_0$ with 95\% confidence.
}

\emptyanswerbox{
    4.2c
}{
    $z_{critical}$: \shortanswerline
}

\question{
    4.2 d
}{
    Calculate the sample \concept{z-value} for the \concept{correlation coefficient} $r_{xy}$.
}

\hint{Hint 4.6: You can find the formula for the \concept{z-value} of a \concept{correlation} in the formula sheet.}

\clearpage % Page break

\emptyanswerbox{
    4.2d
}{
    $z_{xy}$: \shortanswerline
}

\question{
    4.2 e
}{
    Draw the conclusion for the manager. Include the following four elements:
    \begin{itemize}
    \item[$\square$] Show how the calculated \concept{z-value} relates to the \concept{critical z-value}.
    \item[$\square$] Discuss whether $H_0$ is rejected or not.
    \item[$\square$] Describe what this tells us about $\rho_{xy}$.  
    \item[$\square$] Describe what type of error is relevant \textit{(type-I or type-II)}.
\end{itemize}
}

\sixlineanswerbox{4.2e}

\clearpage % Page break