%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Grading sheet: Practical assignment
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Practical assignment}

\fontfamily{pcr}\selectfont 

\begin{center}
\small
\begin{tabularx}{\textwidth}{l|l|>{\raggedright\arraybackslash}X}
    \textbf{Question} & \textbf{Points} & \textbf{Criteria} \\
    \hline
     1a & 1 point & The table contains all the correct metrics, with correct values in the right formatting. \\
     1b & 1 point & The plot shows summary statistics for a relevant subset of the data. \\
     1c & 1 point & The discussion considers sample size and causality, and how different values of categorical variables affect the observations. \\
     2a & 1 point & A figure is made containing all possible combinations of data on a chart. Where trends are suggested by the plots, these are highlighted and discussed. \\
     2b & 1 point & The research questions involve one test of means or proportions, and one regression analysis. \\
     2c & 1 point & The correct variables are researched using the right test with appropriate parameters. \\
     3a & 1 point & It is explained clearly and correctly why and how the test is suitable. \\
     3a & 1 point & The hypotheses are correctly formulated in terms of the parameters in the research question. \\
     3b & 1 point & The right formulas are selected, and the calculation is explained clearly. \\
     3b & 1 point & Correct calculation of appropriate corresponding test statistic. \\
     3c & 1 point & Correct definition of critical region for test statistic. \\
     3c & 1 point & Correct conclusion is drawn, formulated in 4 parts, and explained using the test statistic and critical region. \\
     4a & 1 point & Correct parameters are selected regarding the research question. \\
     4a & 1 point & The hypotheses are correctly formulated. \\
     4b & 1 point & Correctly performed linear regression using \texttt{R} (check on R code). \\
     4b & 1 point & Relevant output and statistics are shown. \\
     4c & 1 point & Interpretation of \texttt{R} results is provided, the test statistic is identified. \\
     4c & 1 point & Correct conclusion is drawn and explained using the test statistic. \\
     5 & 1 point & Correct discussion of generalization of results with respect to representativeness. \\
     5 & 1 point & Correct interpretation on the type I/II risks that apply to the conclusions. \\
     \hline
     \textbf{Total} & 20 points & \\
\end{tabularx}
\end{center}

\normalfont

\clearpage % Page break